Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-08 paper/ms.tex
update ms

% upon AAS submission
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
\documentclass[11pt,twocolumn,tighten]{aastex63}
\turnoffedit

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves for three CPVs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
    (TIC~402980664; Sector~19), TIC~94088626 (Sector 10), and
    TIC~425933644 (Sector~28).
		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
		clump scenario (left) and gas prominence scenario (right) both invoke
		magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

>>>>

% upon AAS submission
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
\turnoffedit

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves for three CPVs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
    (TIC~402980664; Sector~19), TIC~94088626 (Sector 10), and
    TIC~425933644 (Sector~28).
    {\it Bottom:} Cartoon configurations for magnetically-entrained
    corotating material.  The dust clump scenario (left) and gas
    prominence scenario (right) propose different opacity sources, and
    different occultation geometries.
	}
	\label{fig:f1}
\end{figure*}
